Weakly informative observations: not the winner

### 2020-02-03 inst/notthewinner.Rmd
typo

In the above, note that the value of `small` is immaterial and the
evaluate has $p+1=p_2\neq 0$.

@@

```{r}
library("partitions")
M <- perms(5)
M <- M[,M[1,] != 1]
SL <- list()
for(i in seq_len(ncol(M))){
	SL[[i]] <- H + order_likelihood(M[,i,drop=TRUE])
}
SL <- as.suplist(SL)
1e4*like_single_list(indep(equalp(SL)),SL)
1e4*like_single_list(indep(maxp(SL)),SL)
```

>>>>

In the above, note that the value of `small` is immaterial and the
evaluate has $p_1=p_2\neq 0$.

@@

```{r}
library("partitions")
M <- perms(5)
SL <- list()
for(i in seq_len(ncol(M))){
	SL[[i]] <- H + order_likelihood(M[,i,drop=TRUE])
}
SL <- as.suplist(SL)
1e4*like_single_list(indep(equalp(SL)),SL)
1e4*like_single_list(indep(maxp(SL)),SL)
```
